---
title: "William Rayo's CV"
author: William Rayo
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
  # Where the CV data lives: one Google Sheet with tabs entries, contact_info, text_blocks.
  # To build from the local csvs instead, use:  value: "data"
  data_location:
    value: "https://docs.google.com/spreadsheets/d/1V3lM1eQ4JJibDTZ-xjmFPBTUH9wrQSD21DGzjgBvigI"
output:
  pagedown::html_resume:
    css: ['resume', 'dd_cv.css']
    self_contained: true
    includes:
      in_header: header.html
---
``` {css, echo=FALSE}
/* Get rid off the sidebar from the second page */
/* (source:https://www.anabellelaurent.com/slides/rladies_pagedown/cvwithpagedown#18 */
.pagedjs_page:not(:first-of-type) {
  --sidebar-width: 0rem;
  --sidebar-background-color: #ffffff;
  --main-width: 7in;
  --decorator-horizontal-margin: 0.2in;
}
```

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis',
  echo = FALSE
)

source("cv_printing_functions.R")

# Read in all data and initialize a CV printer object.
# data_location is the "data" folder of csvs, or a Google Sheet URL
# (set it in the params at the top of this file).
CV <- create_CV_object(
  data_location = params$data_location,
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================


Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV <- print_contact_info(CV)
```

Updated `r format(Sys.Date(), "%B %Y")`


Main
================================================================================

William Rayo, Ph.D. {#title}
--------------------------------------------------------------------------------

&nbsp;Curriculum Vitae

```{r}
# Optional: add a row with loc = "intro" to text_blocks to show a paragraph here
CV <- print_text_block(CV, "intro")
```


Positions and Appointments {data-icon=building-columns data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'appointments')
```


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'education')
```


Interests {.no-timeline data-icon=lightbulb}
--------------------------------------------------------------------------------

```{r}
# Optional: add a row with loc = "interests" to text_blocks to show a paragraph here
CV <- print_text_block(CV, "interests")
CV <- print_list(CV, 'interests')
```


Awards and Honors {data-icon=award data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'awards')
```


Teaching Experience: Instructor of Record {data-icon=chalkboard-user}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'teaching_ior')
```


Graduate Teaching Experience {data-icon=person-chalkboard}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'teaching_grad')
```


Secondary Teaching {data-icon=school}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'teaching_secondary')
```


Mentorship {data-icon=user-graduate}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'mentorship')
```


Publications {data-icon=book}
--------------------------------------------------------------------------------

<p class="section-note">&#42; denotes student author</p>

```{r}
CV <- print_section(CV, 'pubs')
```


Presentations {data-icon=microphone}
--------------------------------------------------------------------------------

<p class="section-note">&#42; denotes student author</p>

```{r}
CV <- print_section(CV, 'presentations')
```


Poster Presentations {data-icon=note-sticky}
--------------------------------------------------------------------------------

<p class="section-note">&#42; denotes student author</p>

```{r}
CV <- print_section(CV, 'posters')
```


Invited Talks, Guest Lectures, and Workshops {data-icon=comments}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'talks')
```


Professional Service {data-icon=handshake-angle}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'prof_service')
```


University and School Service {data-icon=people-group}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'uni_service')
```


Certifications and Specialized Training {data-icon=certificate data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV <- print_section(CV, 'training')
```


Technical Skills {.no-timeline data-icon=laptop-code}
--------------------------------------------------------------------------------

```{r}
CV <- print_list(CV, 'skills')
```


Organization Affiliations {.no-timeline data-icon=users}
--------------------------------------------------------------------------------

```{r}
CV <- print_list(CV, 'affiliations')
```


```{r}
# Only prints when pdf_mode = TRUE (links become numbered footnotes)
CV <- print_links(CV)
```
